\newpage
\begin{center}
{\Large \textbf{ACKNOWLEDGMENTS}}
\end{center}
\vspace{10mm}

No matter how many, words are pale compare to such friendship between Dr. Mahoor and I. Without his help and support, I might have been lost in my life and looking for something that I do not even know. However, with his help, I found my path and can roam in the scientific field, pursue novel ideas, and seek solutions. I cannot forget the very first day when Dr. Mahoor introduced me to NAO, the robot who I worked with. Thanks to Dr. Mahoor, who provided me with such and exceptional experience and helped me gain knowledge in the filed of Electrical and Computer Engineering and particularly Robotics!

\vspace{3mm}

More than everyone, I indebted to my mother for her enthusiastic encouragement, prayers, and unlimited support during all stages of my life. Understanding and tolerance helped us while argues and fights happened between us. I could not accomplish this work without her selfless love and assistance. Also, I must express my appreciation to my girlfriend, who stands beside me to conquer the very dark time.

\vspace{3mm}

In the past eight years, I have been working with these special children and I cannot stop thinking of their future life after ten years or even more. The honor goes to my late friend, Mr. Masoud Bahramisharif, without his help, I was not able to even begin this project. Mr. Hosein M Golshan provided his endless support for this fantastic work as well, which helps me to complete it on time. I also want to send my appreciation to all the committee members, Dr. Kimon Valavanis, Dr. Tim Sweeney, and Dr. Matthew Rutherford. I would thank them all for their support and serving on my defense committee.

\vspace{3mm}

I again would like to thank my advisor Dr. Mahoor, for providing me such a unique opportunity to work with NAO and supporting me for all these years working on my dissertation. Meanwhile, I want to thank the supports and help I have received from Dr. Anibal Gutierrez from the University of Miami and also Dr. Tim Sweeney and Ms. Francesca Dino from the DU psychology department. I also want to appreciate all my lab mates who gave me lots of courage and motivation and to complete this research.

\vspace{3mm}
Extended thanks to the faculty and staff members of the Electrical and Computer Engineering Department at the University of Denver, especially Ms. Molly Dunn and Ms. Drusell May, for their role in my education and various resources made available to me with my work. Also, I would like to thank my fellow lab members, especially, Dan Stoianovici, Hojjat Abdollahi, Rohola Zandie, Behzad Hasani, and Jian Sun, for their collaboration during the completion of this dissertation.

\vspace{3mm}
Furthermore, I want to thank Dr. Amin Khodaei, Dr. Gonçalo Martins, and Dean J.B. Holston for their support and help during my study at the University of Denver. Being a student and a researcher at DU is the best luck of my life!