\newpage
\vspace*{2.5in}
\begin{center}
\emph{To my beloved mother, deceased father,\\
and \\ to my lovely wife.}
\end{center}

\newpage
\begin{center}
{\Large \textbf{ACKNOWLEDGMENTS}}
\end{center}
\vspace{10mm}

First, I would like to express my sincere gratitude to Professor
Abdel-Mottaleb, who introduced me to the field of computer vision,
and helped me to jump start my research career in this field. He
encouraged me to pursue novel ideas and provided me with exceptional
experience and knowledge.

\vspace{3mm}

My thanks also go to the other members of the committee, Dr.
Shahriar Negahdaripour, Dr. James W. Modestino, Dr. Kamal
Premaratne, and Dr. Ahmad El-gammal for their valuable comments and
suggestions. In particular, I want to thank Dr. Negahdaripour for
his valuable support, comments and encouragement during my Ph.D
study.

\vspace{3mm}

More than everyone, I indebted to my mother for her enthusiastic
encouragement, prayers and unlimited support during all stages of my
life. Also, I must express my appreciation to my beloved wife,
Eshrat, my brothers and sisters.

\vspace{3mm} I would like to extend my thanks to the faculty and
staff members of the Electrical and Computer Engineering Department
at the University of Miami, especially Ms. Clarisa Alvarez and Ms.
Rosamund Coutts for their role in my education and various resources
made available to me to do my research.

Also, I would like to thank my fellow lab members, specially, Dr.
Nasser Al-Ansari, Dr. Pezhman Firoozfam, Dr. Omaima Nomir, Dr.
Charay Leurdwick, Hamed Pirsiavash, Feng Niu, Ali Taatian, Steven
Cadavic, Jindan Zhou, Hossein Madjidi, Behzad M. Dogahe, Dr.
Hongsheng Zhang, Muhammad Rushdi, and Dr. Nuno Gracias for their
collaboration during the completion of this thesis.

\vspace{3mm} In addition, I want to thank Dr. Tapia, Dr. Asfour, and
Mr. Ali Habashi for their support and help during my study at the
University of Miami.
